### 2019-08-26 README.Rmd
Added detailed version of analysis pipeline flowchart to README

development of methods and software for differential enrichment analysis

>>>>

```{r, echo=FALSE, fig.cap='Figure 1. diffEnrich analysis pipeline.', dpi=400}
suppressMessages(library(diagram))

## open plot
par(mar = c(0.5, 0.5, 0.5, 0.5))
openplotmat()
## define number of boxes at each level
elpos <- coordinates (c(3, 1, 1, 2, 2, 1, 1, 1))
## generate matrix of from-to arrow coordinates
fromto <- matrix(ncol = 2, byrow = TRUE,
                 data = c(1, 6,
                          2, 4,
                          3, 7,
                          4, 5,
                          5, 6,
                          5, 7,
                          6, 8,
                          7, 9,
                          8, 10, 
                          9, 10,
                          10, 11,
                          11, 12))
nr <- nrow(fromto)
arrpos <- matrix(ncol = 2, nrow = nr)

## Build flow chart
for (i in 1:nr){
  arrpos[i, ] <- straightarrow (to = elpos[fromto[i, 2], ],
                                from = elpos[fromto[i, 1], ],
                                lwd = 2, arr.pos = 0.6, arr.length = 0.5)
  textellipse(elpos[1,], 0.10, 0.04, lab = "geneList1", box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[2,], 0.10, 0.03, lab = "get_kegg()", box.col = "steelblue1",
              shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[3,], 0.10, 0.04, lab = "geneList2", box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textround(elpos[4,], 0.10, 0.03,lab = "KEGG REST API", box.col = "orange1",
            shadow.col = "orange4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[5,], 0.15, 0.04, lab = c("cleaned gene-to-pathway", "map"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[6,], 0.10, 0.03,lab = "pathEnrich(List 1)", box.col = "steelblue1",
            shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[7,], 0.10, 0.03, lab = "pathEnrich(List 2)", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[8,], 0.10, 0.04, lab = c("pathEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[9,], 0.10, 0.04, lab = c("pathEnrich","result/object"),box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[10,], 0.10, 0.03, lab = "diffEnrich()", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[11,], 0.10, 0.04, lab = c("diffEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[12,], 0.11, 0.03, lab = "plotFoldEnrichment", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  text(0.15,0.05, "Figure 1. diffEnrich Analysis pipeline", cex = 0.75)
}
```

## Introduction

## Differential Enrichment in practice
